---
title: "Gnorm: A new centrality index designed for multilayer networks"
output: html_document
date: "2023-06-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# TUTORIAL

Supplement to the paper: Lotfi N, Requejo HS, Rodrigues F, Mello MAR. A new centrality index for multilayer networks. *In prep*.

*Authors: Nastaran Lotfi, Henrique S. Requejo, Francisco A. Rodrigues & Marco A. R. Mello.*

[Ecological Synthesis Lab](https://marcomellolab.wordpress.com) (SintECO), University of São Paulo.

Contact: [*nas.naslot\@gmail.com*](mailto:nas.naslot@gmail.com){.email}{.email} OR [*marmello\@usp.br*](mailto:marmello@usp.br){.email}{.email}

See [README](https://github.com/Nastaranlotfi/Gnorm-new-centrality-index-multilayer-networks/blob/main/README.md) for further info.

## Summary

1.  [Preparing the data](#data)
2.  [Network construction](#network)
3.  [GNORM Calculation](#Gnorm)
4.  [Source studies](#studies)

## 1. Setting the stage  {#data}

Set the working directory:

```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

Delete all previous objects:

```{r}
rm(list= ls())
```

Load the required packages and functions:

```{r}
library(akima)


library(plyr)
library(dplyr)
library(ggplot2)
library(igraph)
library(multinet)
library(png)
library(RColorBrewer)
```

Create the output folders:

```{r}

rm(list= ls())

if (!dir.exists(path = "data")){
  dir.create(path = "data")
} else {
  print("Dir already exists!")
}

if (!dir.exists(path = "input")){
  dir.create(path = "input")
} else {
  print("Dir already exists!")
}

if (!dir.exists(path = "figures")){
  dir.create(path = "figures")
} else {
  print("Dir already exists!")
}

if (!dir.exists(path = "results")){
  dir.create(path = "results")
} else {
  print("Dir already exists!")
}

currentTime_start <- Sys.time()
```

Source the auxiliary functions:

```{r}

source("Aux_functions.R", encoding="utf-8")
```

Load the data:

```{r}
data = read.csv("input/links_clean.csv", header=T, as.is=T)
```

Inspect the data:

```{r}
head(data)
tail(data)

currentTime_prep <- Sys.time()
```

Define the edge list of the network:

```{r}
Fruit1 <- list()
Fruit2 <- list()
Fruit3 <- list()
Fruit4 <- list()
Nectar1 <- list()
Nectar2 <- list()
Nectar3 <- list()
Nectar4 <- list()

leng<-dim(data)[1]
k2=1
k1=1
for (i in 1:leng) {
	if(data[[i,3]]=="Frugivory"){
		Fruit1[k1]<-c(data[[i,1]])
		Fruit2[k1]<-c(data[[i,2]])
		Fruit3[k1]<-c(1)
		Fruit4[k1]<-c(data[[i,3]])
		#cat('hi',"\n")
		k1=k1+1
		}
	if(data[[i,3]]=="Nectarivory"){
		Nectar1[k2]<-c(data[[i,1]])
		Nectar2[k2]<-c(data[[i,2]])
		Nectar3[k2]<-c(2)
		Nectar4[k2]<-c(data[[i,3]])
		
		k2=k2+1
		}
		
	}


Fruit<-list()
Nectar<-list()
Fruit<-cbind(Fruit1,Fruit2,Fruit3,Fruit4)
Nectar<-cbind(Nectar1,Nectar2,Nectar3,Nectar4)

Links<-rbind(Fruit,Nectar)
colnames(Links) <- c("from","to", "layer_num", "layer")

dim(Links)
head(Links)
tail(Links)

currentTime_link <- Sys.time()
cat('end_link_construction', "\n")

```

Define the node list of the network:

```{r}
name1=unique(data$CurrentBatSpecies)
name1<- name1[order(name1) ]

Fa1=rep("Bats",length(name1))
Fa2=rep(1,length(name1))
Fa3=rep(1,length(name1))

name2=unique(data$CurrentPlantSpecies)
name2<- name2[order(name2) ]

Na1=rep("Plants",length(name2))
Na2=rep(2,length(name2))
Na3=rep(1,length(name2))


Fa<-cbind(name1,Fa1,Fa2,Fa3)
Na<-cbind(name2,Na1,Na2,Na3)

Nodes<-rbind(Fa,Na)
colnames(Nodes) <- c("name","taxon","taxon.label","species.size")

dim(Nodes)
head(Nodes)
tail(Nodes)
```

Save the nodes and links:

```{r}
write.csv(Nodes,"data/nodes1.csv", row.names = FALSE)
write.csv(Links,"data/links1.csv", row.names = FALSE)

currentTime_node <- Sys.time()
cat('end_node_construction', "\n")

```

## 2. Building the network {#network}

Finding the giant component:

```{r}

nodes1 = read.csv("data/nodes1.csv", header=T, as.is=T)
links1 = read.csv("data/links1.csv", header=T, as.is=T)


net_mono1 = graph_from_data_frame(d = links1, vertices = nodes1, directed = F)

c=clusters(net_mono1, mode="weak") #finding the clusters
b=which.max(c$csize) #find the max
v=V(net_mono1)[c$membership!=b] #find the names of nodes in the max component

b1=split(names(v),v) #formating the v file into a list
b2=list()
for (i in 1:length(b1)){
	b2=append(b2,b1[[i]])}

b2=unlist(b2)

df1<-nodes1
df2<-links1

for (i in 1:length(b2)){#remove the nodes that don't belong to the max component
	df1<-df1 %>% filter(!name==b1[i])}

for (i in 1:length(b2)){#removing the links related to the removed nodes
	df2<-df2 %>% filter(!from==b1[i])
	df2<-df2 %>% filter(!to==b1[i])}
	
	
write.csv(df1,"data/nodes2.csv", row.names = FALSE)
write.csv(df2,"data/links2.csv", row.names = FALSE)

currentTime_compo <- Sys.time()
cat('end_names_filtering-by-max-component', "\n")

```

Building multilayer networks for both the empirical network and its giant component:

```{r}

# Complete network #1
nodes1 = read.csv("data/nodes1.csv", header=T, as.is=T)
links1 = read.csv("data/links1.csv", header=T, as.is=T)

nodes1 = nodes1[order(nodes1$name),] 

net_multinet1 = Convert_to_Multinet(nodes1, links1)


# The giant component of the network #2
nodes2 = read.csv("data/nodes2.csv", header=T, as.is=T)
links2 = read.csv("data/links2.csv", header=T, as.is=T)

nodes2 = nodes2[order(nodes2$name),] 

net_multinet2 = Convert_to_Multinet(nodes2, links2)


# Compare the complete network to its giant component
net_multinet1
net_multinet2


currentTime_netcons <- Sys.time()
cat('end_network_construction', "\n")
```

To have a view of the network, we plot both the real network, and the network constructed with the giant component:

```{r}

links_no_dupl1 = links1[-which(duplicated(links1[,c("from", "to")])==T),] 
net_layout1 = graph_from_data_frame(d = links_no_dupl1,
                                   vertices = nodes1, directed = F) 
layout1 = layout_nicely(net_layout1) 

png(filename="figures/network_visualization_complete.png", 
    res = 300, width = 4000, height = 2200)
Custom_plot2D(links1, nodes1, layout1, vertex_label_cex = NULL, vertex_size = 3)
dev.off()


# The giant component of the network #2
links_no_dupl2 = links2[-which(duplicated(links2[,c("from", "to")])==T),] 
net_layout2 = graph_from_data_frame(d = links_no_dupl2,
                                   vertices = nodes2, directed = F) 
layout2 = layout_nicely(net_layout2) 

png(filename="figures/network_visualization_component.png", 
    res = 300, width = 4000, height = 2200)
Custom_plot2D(links2, nodes2, layout2, vertex_label_cex = NULL, vertex_size = 3)
dev.off()



Custom_plot2D(links1, nodes1, layout1, vertex_label_cex = NULL, vertex_size = 3)
Custom_plot2D(links2, nodes2, layout2, vertex_label_cex = NULL, vertex_size = 3)

currentTime_netvis <- Sys.time()
cat('end_network_visualization', "\n")
```

## 3. Calculating Gnorm {#Gnorm}

In the rest of the analysis, we work with the giant component. In the following, we define the main parameter to calculate the Gnorm and find the Gnorm:

```{r}

# Partitioning, omega, gamma, and number of iterations (for getting the mean)
partitions_of_omega = 10 #Number of partitions
seq_G = Create_seq_G_Merged(net_multinet2, partitions_of_omega)
vec_W = Create_vec_W(partitions_of_omega)
gamma_min = 0.25
gamma_max = 4
gamma_spacing = 0.25
gammas = seq(from = gamma_min, to = gamma_max, by = gamma_spacing)
iterations = 100 #It takes a long time, but for stable results use at least 100

# Saving lists definition
Seq_G_Mean_gamma_list = list() 
G_norm_list = list()

# G_analysis
cont_perc = 1 # Calculation of running progress

for (gamma_index in 1:length(gammas)) {
	start_time <- round(as.numeric(Sys.time()))
  	seq_G_list = list()
    	for (i in 1:iterations) {
    		seq_G_list[[i]] = Create_seq_G_Merged(net_multinet2, 
    		                                      partitions_of_omega,
    		                                      gamma = gammas[gamma_index])
    		                                      
    		#####Run-time approximation
    		if (cont_perc==1 ){
    			end_time <- round(as.numeric(Sys.time()))
			time_taken <- round(end_time - start_time,2)
			print (time_taken)
		
			cat("Estimated time needed for run (secs): ", time_taken*(iterations*length(gammas)),"\n" )}
			#cat("\n")}
			#print (time_taken)
		
    		cat(cont_perc*100/(iterations*length(gammas)), "%  ")###print the run progress
    		cont_perc = cont_perc + 1
  		}#end of iterations
  
  
  #Removing names
  	seq_G_list_no_names = list()
  	for (i in 1:length(seq_G_list)) {
		seq_G_list_temp = seq_G_list[[i]]
		seq_G_list_temp[,1] = 1
		seq_G_list_no_names[[i]] = seq_G_list_temp
  		}#end of seg_G_list
  
  #Summation of Gvalues during the iteration
  	seq_G_sum = seq_G_list_no_names[[1]]
	for (i in 2:length(seq_G_list)) {
		seq_G_sum = seq_G_sum + seq_G_list_no_names[[i]]
		}#end of sum for 100 iterations
		#seq_G_sum
  
  	#Finding the mean-G_value over iteration
	seq_G_mean = seq_G_sum / iterations
  
  	#Adding names
	seq_G_mean[,1] = seq_G_list[[1]]$actor
  
  	#STD-calculation
	seq_G_StdDev = StdDev_list_of_seq_G(seq_G_list)
  
  	#Sorting with G_norm
	nodes_G_norm = Sort_Nodes_by_Total_G(seq_G_mean, ordered = FALSE)
	nodes_G_norm_Ordered = Sort_Nodes_by_Total_G(seq_G_mean, ordered = TRUE)

  	#Saving G_values respect to gamma
	Seq_G_Mean_gamma_list[[gamma_index]] = cbind(seq_G_mean, gammas[gamma_index])
	G_norm_list[[gamma_index]] = nodes_G_norm
  
	}#end of gamma

##Finding mean over Gamma
G_norm_sum = G_norm_list[[1]]
for (i in 2:length(G_norm_list)) {
	G_norm_sum = G_norm_sum + G_norm_list[[i]]
	}
G_norm_mean = G_norm_sum / (length(G_norm_list))

##Sorting G_norm_mean
G_norm_mean_ordered =  sort(G_norm_mean, decreasing = TRUE)

save(gammas, vec_W, iterations, partitions_of_omega, links2, nodes2,
     Seq_G_Mean_gamma_list,G_norm_mean, G_norm_mean_ordered,
     file = "results/Bat_Net.RData")

currentTime_Gnorm <- Sys.time()
cat('end_Gnorm', "\n")

```

Reference

-   Lofti N, Requejo HS, Rodrigues FA, Mello MAR. A new centrality index for multilayer networks. *In prep*.

Source repos

[TF](https://github.com/marmello77/TF)

## 4. Source studies {#studies}

-   Bianconi, G. (2018). Multilayer networks: Structure and function. Oxford University Press. <http://dx.doi.org/10.1093/oso/9780198753919.001.0001>

-   Blondel, V. D., Guillaume, J.-L., Lambiotte, R., & Lefebvre, E. (2008). Fast unfolding of communities in large networks. Journal of Statistical Mechanics: Theory and Experiment, 2008(10), P10008. <https://doi.org/10.1088/1742-5468/2008/10/p10008>

-   Mello, M., Rodrigues, F., Costa, L., Kissling, W., Şekercioğlu, Ç., Marquitti, F., & Kalko, E. (2014). Keystone species in seed dispersal networks are mainly determined by dietary specialization. Oikos, 124(8), 1031--1039. <https://doi.org/10.1111/oik.01613>

-   Mello, M. A. R., Felix, G. M., Pinheiro, R. B. P., Muylaert, R. L., Geiselman, C., Santana, S. E., Tschapka, M., Lotfi, N., Rodrigues, F. A., & Stevens, R. D. (2019). Insights into the assembly rules of a continent-wide multilayer network. Nature Ecology & Evolution, 3(11), 1525--1532. <https://doi.org/10.1038/s41559-019-1002-3>

-   Mucha, P. J., Richardson, T., Macon, K., Porter, M. A., & Onnela, J.-P. (2010). Com- munity structure in time-dependent, multiscale, and multiplex networks. Science, 328(5980), 876--878. <https://doi.org/10.1126/science.1184819>

-   Pilosof, S., Porter, M. A., Pascual, M., & Kéfi, S. (2017). The multilayer nature of ecological networks. Nature Ecology & Evolution, 1(4). <https://doi.org/10.1038/s41559-017-0101> \`\`\`
